Extracting data for time slice analyses

### 2017-11-27 analyses/01-extract-data-for-analyses.Rmd
Add names to readRDS objects

```{r, eval = FALSE}
## Estimating the ancestral states (with a uncertainty threshold of 0.95)
matrix_nodes <- AncStateEstMatrix(matrix, tree, estimate.allchars = TRUE,
                                  uncertainty.threshold = 0.95)

@@

```{r}
## Loading the matrix
readRDS(paste0("../data/processed/ancestral_states.", slug ,".Rda"))

@@

## Add ancestral states to nodes
readRDS(paste0("../data/processed/ancestral_states.", slug ,".Rda"))
row.names(matrix_nodes) <- tree$node.label
matrix$matrix <- rbind(matrix$matrix, matrix_nodes)

>>>>

```{r, eval = FALSE}
## Estimating the ancestral states (with a uncertainty threshold of 0.95)
## This is slow, so on future runs we recommend using the saved data
matrix_nodes <- AncStateEstMatrix(matrix, tree, estimate.allchars = TRUE,
                                  uncertainty.threshold = 0.95)

@@

```{r}
## Loading the matrix
## Not needed if running all the code at once
## matrix_nodes <- readRDS(paste0("../data/processed/ancestral_states.", slug ,".Rda"))

@@

## Add ancestral states to nodes
## matrix_nodes <- readRDS(paste0("../data/processed/ancestral_states.", slug ,".Rda"))
row.names(matrix_nodes) <- tree$node.label
matrix$matrix <- rbind(matrix$matrix, matrix_nodes)
